Reproducing Analyses for Phenotypic evolution is less constrained in complex

### 2018-10-24 analyses/reproduce_analyses.Rmd
changed from log1p to sqrt transformation of female preference

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots))))

@@

mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq", univariatePlot = "histogram")

# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq")

@@

```{r Model 1, cache=TRUE}
model_1 <- glmer(
  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +
    Foodweb:(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

We use parametric bootstrapping (n=`r n_boots_analysis`) to evaluate the statistical significance of the effect of food-web treatment on nonlinear terms (i.e. Foodweb:trait^2 or Foodweb:trait_1:trait_2). Food-web treatment does influence the quadratic effect of of female preference on larva survival. None of the other terms statistically differ from zero.

@@

tidy_model_1 <- tidy(boot_model_1, conf.int=T) %>% 
  # filter terms that only matter for this analysis
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) 
```

@@

plot_model_1$term_plot <- factor(plot_model_1$term,
                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"),
                                ordered=TRUE)

plot_model_1 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_1$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

model_2 <- update(model_1, 
                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2)
                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
```

@@

tidy_model_2 <- tidy(model_2, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebSimple:I(sc.log1p.Pref^2)")) 
```

@@

```{r Plot Nonlinear Terms, echo=FALSE}
tidy_model_2$term_plot <- factor(tidy_model_2$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
                            ordered = TRUE)

tidy_model_2 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(tidy_model_2$term_plot))) +
  ylab("Coefficient (logit scale)")
```

Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.log1p.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient. To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope. See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
```{r Adjust Model 2 for Slopes}
model_2_adj <- update(model_2, .~. -I(sc.log1p.Pref^2))
```

```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE}
boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

tidy_model_2_adj <- tidy(model_2_adj, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"))
```

@@

```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE}
tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
                            ordered = TRUE)

@@

```{r Fit Model 3, cache=TRUE}
model_3 <- update(model_2, 
                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -Foodweb:I(sc.log1p.Pref^2) 
                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref)
```

@@

tidy_model_3 <- tidy(boot_model_3, conf.int=T) 
```

Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.high,2)`).

@@

plot_model_3$term_ord <- factor(plot_model_3$term, 
                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"),
                                ordered = TRUE)
plot_model_3 %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(limits=rev(levels(plot_model_3$term_ord))) +
  ylab("Coefficient (logit scale)")
```

@@

```{r Fit Model 4, cache=TRUE}
model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
```

@@

tidy_model_4 <- tidy(boot_model_4, conf.int=T) 
```

```{r Plot Model 4, echo=FALSE}
tidy_model_4$term_plot <- factor(tidy_model_4$term, 
                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
                                ordered = TRUE)

@@

plot_model_4 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_4$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

tidy_model_4_adj <- tidy(boot_model_4_adj, conf.int=T) 
```

```{r Plot adjusted model 4, echo=FALSE}
tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
                                ordered = TRUE)

@@

plot_model_4_adj %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_4_adj$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

tidy_model_4_survival_ests <- tidy(boot_model_4_survival_ests, conf.int=T)

tidy_model_4_survival_ests
```

@@

Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.log1p.Pref) and sc.log.Clutch. Here, we need the different coefficients.

@@

```{r Organize and Transform Coefficients, include=FALSE}
tidy_coefs <- bind_rows(
  select(tidy_model_2_adj, term, estimate, conf.low, conf.high), 
  select(tidy_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
  filter(term != "(Intercept)", term != "FoodwebSimple") # remove main effects

# Tidy common coefficients
tidy_common_coefs <- tidy_coefs %>%
  filter(term!="FoodwebComplex:I(sc.log1p.Pref^2)", term!="FoodwebSimple:I(sc.log1p.Pref^2)",
         term!="FoodwebComplex:sc.log.Clutch",term!="FoodwebSimple:sc.log.Clutch")

# Tidy unique coefficients to each food-web
complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.log1p.Pref^2)")
complex_quad_pref$term <- "I(sc.log1p.Pref^2)"
simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.log1p.Pref^2)")
simple_quad_pref$term <- "I(sc.log1p.Pref^2)"

@@

tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_quad_pref, simple_clutch) %>%
  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al. 2008)
  transmute(term=term,
            gradient = simple_mean_brackets * estimate / simple_mean_fitness * Multiplier,
            `2.5%` = simple_mean_brackets * conf.low / simple_mean_fitness * Multiplier,
            `97.5%` = simple_mean_brackets * conf.high / simple_mean_fitness * Multiplier)

tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_quad_pref, complex_clutch) %>%
    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al. 2008)
  transmute(term=term,
            gradient = complex_mean_brackets * estimate / complex_mean_fitness * Multiplier,
            `2.5%` = complex_mean_brackets * conf.low / complex_mean_fitness * Multiplier,
            `97.5%` = complex_mean_brackets * conf.high / complex_mean_fitness * Multiplier)

@@

```{r Table of Selection Gradients, echo=FALSE}
selection_gradients$term_ord <- factor(selection_gradients$term, 
                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
                                   ordered = TRUE)

@@

tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebLarval:I(sc.log1p.Pref^2)")) 
```

@@

```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
                            ordered = TRUE)

tidy_egg.larval_model_2 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2$term_plot))) +
  ylab("Coefficient (logit scale)")
```
 To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE}
egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
```

```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE}

@@

tidy_egg.larval_model_2_adj <- tidy(egg.larval_model_2_adj, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref")) 
```

@@

tidy_egg.larval_model_4 <- tidy(boot_egg.larval_model_4, conf.int=T) 
```

>>>>

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(Density_per_100_shoots))))

@@

mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq", univariatePlot = "histogram")

# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")

@@

```{r Model 1, cache=TRUE}
model_1 <- glmer(
  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

We use parametric bootstrapping (n=`r n_boots_analysis`) to evaluate the statistical significance of the effect of food-web treatment on nonlinear terms (i.e. Foodweb:trait~i~^2^ or Foodweb:trait~i~:trait~j~). Food-web treatment does influence the quadratic effect of of female preference on larva survival. None of the other terms statistically differ from zero.

@@

tidy_model_1 <- tidy(model_1, conf.int=T) %>% #tidy(boot_model_1, conf.int=T) %>% 
  # filter terms that only matter for this analysis
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref")) 
```

@@

plot_model_1$term_plot <- factor(plot_model_1$term,
                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref"),
                                ordered=TRUE)

plot_model_1 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), shape=21, size=3, fill="grey") + # y=statistic for bootstrap
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_1$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

model_2 <- update(model_1, 
                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.sqrt.Pref^2)
                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.sqrt.Pref -Foodweb:sc.log.Clutch:sc.sqrt.Pref)
```

@@

tidy_model_2 <- tidy(model_2, conf.int=T) %>% # tidy(boot_model_2, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
                     "FoodwebSimple:I(sc.sqrt.Pref^2)")) 
```

@@

```{r Plot Nonlinear Terms, echo=FALSE}
tidy_model_2$term_plot <- factor(tidy_model_2$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                            ordered = TRUE)

tidy_model_2 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) + # y=statistic
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(tidy_model_2$term_plot))) +
  ylab("Coefficient (logit scale)")
```

Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.sqrt.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient. To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope. See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
```{r Adjust Model 2 for Slopes, eval=FALSE}
model_2_adj <- update(model_2, .~. -I(sc.sqrt.Pref^2))
```

```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE, eval=FALSE}
boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

tidy_model_2_adj <- tidy(model_2_adj, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))
```

@@

```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE, eval=FALSE}
tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                            ordered = TRUE)

@@

```{r Fit Model 3, cache=TRUE}
model_3 <- update(model_2, 
                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.sqrt.Pref^2) #-Foodweb:I(sc.sqrt.Pref^2) 
                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.sqrt.Pref -sc.log.Clutch:sc.sqrt.Pref)
```

@@

tidy_model_3 <- tidy(model_3, conf.int=T) # boot_model_3
```

Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.high,2)`).

@@

plot_model_3$term_ord <- factor(plot_model_3$term, 
                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.sqrt.Pref"),
                                ordered = TRUE)
plot_model_3 %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(limits=rev(levels(plot_model_3$term_ord))) +
  ylab("Coefficient (logit scale)")
```

@@

```{r Fit Model 4, cache=TRUE}
model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.sqrt.Pref)
```

@@

tidy_model_4 <- tidy(model_4, conf.int=T) # boot_model_4
```

```{r Plot Model 4, echo=FALSE}
tidy_model_4$term_plot <- factor(tidy_model_4$term, 
                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
                                ordered = TRUE)

@@

plot_model_4 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_4$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

tidy_model_4_adj <- tidy(model_4_adj, conf.int=T) # boot_model_4_adj
```

```{r Plot adjusted model 4, echo=FALSE}
tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
                                ordered = TRUE)

@@

plot_model_4_adj %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_model_4_adj$term_plot))) +
  ylab("Coefficient (logit scale)")
```

@@

tidy_model_4_survival_ests <- tidy(model_4_survival_ests, conf.int=T) # boot_model_4_survival_ests

round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$estimate),2) # statistic
round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$estimate),2) # statistic
```

@@

Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.sqrt.Pref) and sc.log.Clutch. Here, we need the different coefficients.

@@

```{r Organize and Transform Coefficients, include=FALSE}
tidy_coefs <- bind_rows(
  select(tidy_model_2, term, estimate, conf.low, conf.high), # estimate=statistic; tidy_model_2_adj no longer needed, since quadratic and correlational selection didn't differ among treatments
  select(tidy_model_4_adj, term, estimate, conf.low, conf.high)) %>% # estimate=statistic
  filter(term != "(Intercept)", term != "FoodwebSimple") # remove main effects

# Tidy common coefficients
tidy_common_coefs <- tidy_coefs %>%
  filter(#term!="FoodwebComplex:I(sc.sqrt.Pref^2)", term!="FoodwebSimple:I(sc.sqrt.Pref^2)",
         term!="FoodwebComplex:sc.log.Clutch",term!="FoodwebSimple:sc.log.Clutch")

# Tidy unique coefficients to each food-web
#complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.sqrt.Pref^2)")
#complex_quad_pref$term <- "I(sc.sqrt.Pref^2)"
#simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.sqrt.Pref^2)")
#simple_quad_pref$term <- "I(sc.sqrt.Pref^2)"

@@

tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_clutch) %>% # simple_quad_pref, 
  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al. 2008)
  transmute(term=term,
            gradient = simple_mean_brackets * estimate / simple_mean_fitness * Multiplier,
            `2.5%` = simple_mean_brackets * conf.low / simple_mean_fitness * Multiplier,
            `97.5%` = simple_mean_brackets * conf.high / simple_mean_fitness * Multiplier)

tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_clutch) %>% # complex_quad_pref, 
    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al. 2008)
  transmute(term=term,
            gradient = complex_mean_brackets * estimate / complex_mean_fitness * Multiplier,
            `2.5%` = complex_mean_brackets * conf.low / complex_mean_fitness * Multiplier,
            `97.5%` = complex_mean_brackets * conf.high / complex_mean_fitness * Multiplier)

@@

```{r Table of Selection Gradients, echo=FALSE}
selection_gradients$term_ord <- factor(selection_gradients$term, 
                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
                                   ordered = TRUE)

@@

tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% # boot_egg.larval_model_2
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))#,
                     #"FoodwebLarval:I(sc.sqrt.Pref^2)")) 
```

@@

```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                            ordered = TRUE)

tidy_egg.larval_model_2 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2$term_plot))) +
  ylab("Coefficient (logit scale)")
```
 To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE, eval=FALSE}
egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
```

```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE, eval=FALSE}

@@

tidy_egg.larval_model_2_adj <- tidy(egg.larval_model_2_adj, conf.int=T) %>% 
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.sqrt.Pref^2)","FoodwebLarval:I(sc.sqrt.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) 
```

@@

tidy_egg.larval_model_4 <- tidy(egg.larval_model_4, conf.int=T) # boot_egg.larval_model_4
```
